---
title: "lesson_1_5_which_city"
format: html
---

First, load the libraries and the data by running the code block below:

```{r}
library(tidyverse)
cities = tibble(
  denver = c(44, 51, 61, 65, 80, 89),
  sf = c(60, 63, 65, 65, 66, 71)
)
cities
```

First, make a histogram of the denver temperatures.

```{r}
cities |> 
  ggplot(aes(x = denver)) +
  geom_histogram(binwidth = 10)
```

To calculate statistics for just the denver temperatures, use the `pull` function:

```{r}
denver_temperatures = 
  cities |> 
  pull(denver)
```

Calculate the mean temperature in Denver:

```{r}
mean(denver_temperatures)
```

Calculate the standard deviation of the temperatures in Denver:

```{r}
sd(denver_temperatures)
```

Calculate the "five number summary":

* The minimum (at 0% of the data)
* The first quartile (at the first 1/4 of the data)
* The median (also called the 2nd quartile, t the first 1/2 of the data)
* The third quartile (at the first 3/4 of the data)
* The maximum (at 100% of the data)

```{r}
quantile(denver_temperatures, c(0, 1/4, 1/2, 3/4, 1))
```

WRITE THESE NUMBERS IN YOUR WORKSHEET, THEN CONTINUE WITH THE WORKSHEET

If you want to make a new code block, use Cmd+Option+i (or Ctrl+Option+i for Windows).

